Probabilistic Catalogs for Crowded Stellar Fields

### 2012-10-31 paper/ms.tex
Anoter reference

Bayesian object detection (as this problem is sometimes called) has been
implemented by \citet{2011MNRAS.415.3462F}
under the assumption of a known number of objects $N$.
This assumption is required for the
{\tt MultiNest} sampler \citep{multinest} to be applicable.
Using the results from the known $N$
run, it is possible (under certain circumstances) to reconstruct what the
results would have been if a variable-$N$ simulation had been used. However,
this will not work well in situations where there is significant confusion
(i.e. two or more sources overlap). What is really required is a variable
dimension model, where $N$ is an unknown quantity to be inferred from the data.
The computational implementation of these models will require tools such as
reversible jump Markov Chain Monte Carlo \citep{rjmcmc}. Other statistical
methods such as maximum likelihood have also been used to model crowded fields
\citep[e.g.][]{irwin}. However, maximum likelihood is not completely appropriate
because it may lead to overfitting. In this situation overfitting would result
in more stars being added to the model to explain small positive fluctuations
in the image which are actually due to noise.

@@

>>>>

Bayesian object detection (as this problem is sometimes called) has been
implemented both inside and outside of astronomy
\citep[e.g.][]{object, 2011MNRAS.415.3462F}. However, the 
\citet{2011MNRAS.415.3462F} approach makes the assumption of a
known number of objects $N$.
This assumption is required for the
{\tt MultiNest} sampler \citep{multinest} to be applicable.
Using the results from the known $N$
run, it is possible (under certain circumstances) to reconstruct what the
results would have been if a variable-$N$ simulation had been used. However,
this will not work well in situations where there is significant confusion
(i.e. two or more sources overlap). What is really required is a variable
dimension model, where $N$ is an unknown quantity to be inferred from the data.
The computational implementation of these models will require tools such as
reversible jump Markov Chain Monte Carlo \citep{rjmcmc}. Other statistical
methods such as maximum likelihood have also been used to model crowded fields
\citep[e.g.][]{irwin}. However, maximum likelihood is not completely appropriate
because it may lead to overfitting. In this situation overfitting would result
in more stars being added to the model to explain small positive fluctuations
in the image which are actually due to noise.

@@

\bibitem[Harkness and Green(2000)]{object} Harkness, M.~A. and Green, P.~J., 2000,
Parallel chains, delayed rejection and reversible jump MCMC for object recognition,
British Machine Vision Conference Proceedings.
